quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-04 paper-quollr.Rmd
usage section and installing packages chunk modified

```{r install-libraries, include=FALSE, warning=FALSE, echo=FALSE}

@@

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:algo-step-html)"} else { "Figure \\@ref(fig:algo-steps)"})`). A detailed description of the algorithm can be found in @gamage2025c.

@@

>>>>

```{r install-libraries, include=FALSE, warning=FALSE, echo=FALSE, eval=FALSE}

@@

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions. A detailed description of the algorithm can be found in @gamage2025c.

@@

which produces the model and data plot(s) shown in `r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:algo-step-html)"} else { "Figure \\@ref(fig:algo-steps)"})`.

### 2025-12-04 paper-quollr.tex
Updated Figure 3
usage section and installing packages chunk modified

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions (Figure \ref{fig:algo-steps}). A detailed description of the algorithm can be found in \citet{gamage2025c}.

@@

@@

The result is a \texttt{tibble} of the scaled \(2\text{-}D\) embedding with an additional \texttt{h} column, indicating the hexagonal bin to which each point belongs.
?

>>>>

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions. A detailed description of the algorithm can be found in \citet{gamage2025c}.

@@

which produces the model and data plot(s) shown in Figure \ref{fig:algo-steps}.

@@

The result is a \texttt{tibble} of the scaled \(2\text{-}D\) embedding with an additional \texttt{h} column, indicating the hexagonal bin to which each point belongs.
